Explore tumor cell classification with CellAssign

### 2024-05-01 analyses/ewings-cell-type/02-cellassign-tumor-cell-classification.Rmd
render notebook

panglao_tumor_ref_mtx <- panglao_tumor_ref_mtx[which(rowsums > 1),]

@@

This is definitely not what I expected... 
It looks like most cells are categorized as "other" with a few categorized as tumor. 
I would have thought that at least some cells would be endothelial or fibroblast.

@@

Again, it looks like cells that were classified as normal are considered tumor here. 
I think if we want to use CellAssign, we will need to spend more time carefully curating a marker gene list that includes all possible cell types for these samples. 
Another alternative is to use the CellAssign annotations that we already have to help guide which cells may be tumor or normal. 
For example, we expect that muscle cells will be tumor cells.

>>>>

panglao_tumor_ref_mtx <- panglao_tumor_ref_mtx[-which(rowsums > 1),]

@@

This is definitely not what I expected... 
It looks like most cells are categorized as "other" with a few categorized as tumor and only 1 endothlial cell. 
I would have thought that at least some cells would be endothelial or fibroblast.

@@

Again, it looks like cells that were classified as normal are considered tumor here. 
I think if we want to use `CellAssign`, we will need to spend more time carefully curating a marker gene list that includes all possible cell types for these samples. 
Another alternative is to use the `CellAssign` annotations that we already have to help guide which cells may be tumor or normal. 
For example, we expect that muscle cells will be tumor cells.
